\begin{itemize}
  \item System will have a server that runs an internally stored OpenFlexure Web API. Connected users will be able to send requests using this Web API.
  \item Users will be able to connect to the system both locally and remotely.
  \item System will have interface for users. Users will be able to navigate microscope stage, view camera livestream, capture images and record videos using this interface. They will also be able to manage and modify the saved media.
  \item System will have interface for system admins. System admins will be able to manage system settings. Additionally, they will be able to view connected users and manage these connections using this interface.
  \item System will have interface for maintainers. Maintainers will be able to view detailed system logs which contain description, time and type information. Additionally, they will be able to check software updates and install these updates to the system using this interface.
  \item System will have interface for maintainers. Maintainers will be able to view detailed system logs which contain description, time and type information. Additionally, they will be able to check software updates and install these updates to the system using this interface.
  \item The system has many information such as connected user IP addresses, admin and maintainer information, saved media and system logs to save to and retrieve from database. To provide secure and stable connection, the system will also have Database Management Interface.
  \item Since microscopes are error-prone systems, to hande these errors system will have Back-end Failure Management Interface. When an error occurs, the system will save the detailed log of this error in the protected area of ​​the database and maintainers will be able view these system failure logs.
\end{itemize}
However,
\begin{itemize}
	\item Designing the hardware components of the OpenFlexure Microscope 
	\item Designing and implementing the OpenFlexure Connect desktop application
	\item Designing and implementing the OpenFlexure Web API
	\item Designing and implementing the OpenFlexure Update System and Update API
\end{itemize}
are out of the scope of this project.